A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-11-19 paper/paper.tex
Improving text

To every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$. Compared to the informal description given in section~\ref{sec:rel-param}, e.g. $X_1 : X_0 \rightarrow X_0 \rightarrow \U$, this amounts to apply the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$.. In particular, $\fullframe[n]$ is a ``telescope'', i.e. a nesting of $\Sigma$-types.

>>>>

To every $X_n$ is uniformly assigned a type of the form $\fullframe[n] \rightarrow \U$. Compared to the informal description given in section~\ref{sec:rel-param}, this amounts to applying the isomorphisms between $A \rightarrow B \rightarrow C$ and $A \times B \rightarrow C$, or between $\Pi a: A.\, (B a \rightarrow C)$ and $(\Sigma a: A.\, B a) \rightarrow C$ so as to get the expected form $\fullframe[n] \rightarrow \U$. In particular, $\fullframe[n]$ is a ``telescope'', i.e. a nesting of $\Sigma$-types.
